Testing atlantisom: true biomass output from Atlantis

### 2019-04-26 TrueBioTest.Rmd
add NOBA files, separate functions

if(initNOBA){
  d.name <- here("atlantisoutput","NOBACERESGlobalSustainability")
  functional.groups.file <- "nordic_groups_v04.csv" 
  biomass.pools.file <- "nordic_biol_v23.nc"
  biol.prm.file <- "nordic_biol_incl_harv_v_007_3.prm"
  box.file <- "Nordic02.bgm"
  initial.conditions.file <- ".nc"
  run.prm.file <- "nordic_run_v01.prm"
  scenario.name <- "nordic_runresults_01"
}

@@

```{r get_truth, message=FALSE, warning=FALSE, eval=FALSE}
#Load functional groups
funct.groups <- load_fgs(dir=d.name,
                         file_fgs = functional.groups.file)
#Get just the names of active functional groups
funct.group.names <- funct.groups %>% 
  filter(IsTurnedOn == 1) %>%
  select(Name) %>%
  .$Name

#Store all loaded results into an R object
results <- run_truth(scenario = scenario.name,
          dir = d.name,
          file_fgs = functional.groups.file,
          file_bgm = box.file,
          select_groups = funct.group.names,
          file_init = initial.conditions.file,
          file_biolprm = biol.prm.file,
          file_runprm = run.prm.file
)

if(initCCA) CCAresults <- results
if(initNEUS) NEUSresults <- results
if(initNOBA) NOBAresults <- results
```

@@

# should return all model areas; need to generalize
if(initCCA)
if(initNEUS) boxall <- c(0:29)
if(initNOBA)

# should return all model output timesteps; need to generalize
if(initCCA)
if(initNEUS) timeall <- c(0:251)
if(initNOBA)

# define set of species we expect surveys to sample (e.g. fish only? vertebrates?)
# for ecosystem indicator work test all species
# to keep plots simpler, currently hardcoded for vertebrate groups
if(initCCA)
if(initNEUS) survspp <- funct.group.names[1:21]
if(initNOBA)

@@

```{r surveyBbased}

@@

```{r surveyNbased}

>>>>

if(initNOBA){
  d.name <- here("atlantisoutput","NOBACERESGlobalSustainability")
  functional.groups.file <- "nordic_groups_v04.csv" 
  biomass.pools.file <- "nordic_biol_v23.nc"
  biol.prm.file <- "nordic_biol_incl_harv_v_007_3.prm"
  box.file <- "Nordic02.bgm"
  initial.conditions.file <- "nordic_biol_v23.nc"
  run.prm.file <- "nordic_run_v01.xml"
  scenario.name <- "nordic_runresults_01"
}

@@

```{r get_names, message=FALSE, warning=FALSE}
#Load functional groups
funct.groups <- load_fgs(dir=d.name,
                         file_fgs = functional.groups.file)
#Get just the names of active functional groups
funct.group.names <- funct.groups %>% 
  filter(IsTurnedOn == 1) %>%
  select(Name) %>%
  .$Name

```{r get_truth, message=FALSE, warning=FALSE, eval = FALSE}
#Store all loaded results into an R object
results <- run_truth(scenario = scenario.name,
          dir = d.name,
          file_fgs = functional.groups.file,
          file_bgm = box.file,
          select_groups = funct.group.names,
          file_init = initial.conditions.file,
          file_biolprm = biol.prm.file,
          file_runprm = run.prm.file
)

if(initCCA) CCAresults <- results
if(initNEUS) NEUSresults <- results
if(initNOBA) NOBAresults <- results

@@

# should return all model areas; need to generalize
if(initCCA) boxall <- c(0:29) #placeholder, correct for CCA
if(initNEUS) boxall <- c(0:29)
if(initNOBA) boxall <- c(0:29) #placeholder, correct for NOBA

# should return all model output timesteps; need to generalize
if(initCCA) timeall <- c(0:251) #placeholder, correct for CCA
if(initNEUS) timeall <- c(0:251)
if(initNOBA) timeall <- c(0:251) #placeholder, correct for NOBA

# define set of species we expect surveys to sample (e.g. fish only? vertebrates?)
# for ecosystem indicator work test all species
# to keep plots simpler, currently hardcoded for vertebrate groups
if(initCCA) survspp <- funct.group.names[1:21] #placeholder, correct for CCA
if(initNEUS) survspp <- funct.group.names[1:21]
if(initNOBA) survspp <- funct.group.names[1:21] #placeholder, correct for NOBA

@@

```{r surveyBbased, eval = FALSE}

@@

```{r surveyNbased , eval = FALSE}
